Inverse conformational selection in lipid-protein binding

### 2021-07-01 manuscriptPGPE.tex
Updates based on reviewer comments

     \includegraphics[height=3.5cm]{../Figs/TOC2.eps}
%Some journals require a graphical entry for the Table of Contents.
%This should be laid out ``print ready'' so that the sizing of the
%text is correct.

@@

MD simulations could be used to interpret the lipid conformational ensembles from experiments due to their direct connection to the measured C-H bond order parameters $S_\mathrm{CH}$. To find the best MD simulation models (force fields) for this purpose, we took advantage of the power of the NMRlipids Project, an open science collaboration that has gathered a massive number of simulation trajectories, allowing the evaluation of all the available force fields of PC~\cite{botan15}, PS~\cite{antila19}, PE (Fig.~\ref{HGorderParametersPE}), and PG (Fig.~\ref{HGorderParametersPOPG}) lipids against NMR data. The comparison of hundreds of simulation trajectories simulated with approximately 20 different force fields revealed that none of them can correctly capture the lipid conformational ensembles and reproduce the experimental $S_\mathrm{CH}$ of all segments within experimental error. However, CHARMM36, the force field showing the best agreement with experiments, correctly captures the essential differences between the PC, PE, PG, and PS headgroup order parameters (compare Figs.~\ref{HGorderParameters}D and \ref{structures} B).

>>>>

     \includegraphics[height=3.5cm]{./Figs/TOC2.eps}
%Some journals require a graphical entry for the Table of Contents.
%This should be laid out ``print ready'' so that the sizing of the
%text is correct.

@@

MD simulations could be used to interpret the lipid conformational ensembles from experiments due to their direct connection to the measured C-H bond order parameters $S_\mathrm{CH}$. To find the best MD simulation models (force fields) for this purpose, we took advantage of the power of the NMRlipids Project, an open science collaboration that has gathered a massive number of simulation trajectories, allowing the evaluation of all the available force fields of PC~\cite{botan15}, PS~\cite{antila19}, PE (Fig.~\ref{HGorderParametersPE}), and PG (Fig.~\ref{HGorderParametersPOPG}) lipids against NMR data. The comparison of hundreds of simulation trajectories simulated with approximately 20 different force fields revealed that none of them can correctly capture the lipid conformational ensembles and reproduce the experimental $S_\mathrm{CH}$ of all segments within experimental error (for detailed discussion on the quality of force fields, see section S3 in the supplementary information and Refs. \citenum{botan15,ollila16,antila19}). However, CHARMM36, the force field showing the best agreement with experiments, correctly captures the essential differences between the PC, PE, PG, and PS headgroup order parameters (compare Figs.~\ref{HGorderParameters}D and \ref{structures} B).
